### 2017-03-23 thesis/discussion/discussion.tex
tmp commit

In the step wise linear models, many variables were identified to be significantly associated with the obesity metagenes.
This suggested that the pathway associated genetic signatures that were signicant in these models may be biologically related to the obesity phenotype, or perhaps the obesity associated genetic signatures were detecting the signals from these pathways rather than the signals from the phenotype.
In fact, many of the variables included in the linear models were pathway metagenes that negatively correlated with the obesity metagenes in \cref{fig:gatza_allmeta} (\cref{sub:comparison_of_the_obesity_and_pathway_associated_signatures}).
Therefore, it may be possible that these pathways (Akt, \gls{er}, \gls{egfr}, \gls{pr}, p53, Src and \gls{tgfb}) are related to the underlying biological mechanism that drives breast tumour development, and potentially associated with the patient \gls{bmi} as well.

With that said, even if these pathway signatures were related to the obesity associated genetic signatures, the fact that these results depended on the pathway associated genetic signatures from the \citet{Gatza2010a} study makes the results questionable.
This was due to the lack of consistency of the metagenes across different cancer data sets, where more than half of the pathway metagenes showed a correlation of less than 0.8 in at least one data set (\cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}).
This meant that at least half of the signatures were specific to the GT data set and could be highly variable in the other data sets, reflecting the potential differences in the cohorts (at the molecular level).
Thus, without further validation of the quality of the pathway associated genetic signatures and verification of the roles of these signatures in the biological relationship between obesity and cancer, these results should be interpreted with care.

>>>>

In the step wise linear models, many variables were identified to be significantly associated with the obesity metagenes.
This suggested that the pathway associated genetic signatures that were signicant in these models may be biologically related to the obesity phenotype, or perhaps the obesity associated genetic signatures were detecting the signals from these pathways rather than the signals from the obesity phenotype.
In fact, many of the variables included in the linear models were pathway metagenes that negatively correlated with the obesity metagenes in \cref{fig:gatza_allmeta} (\cref{sub:comparison_of_the_obesity_and_pathway_associated_signatures}).
Since all of the obesity metagenes failed to show significant association with patient \gls{bmi}, it may be possible that these pathways (Akt, \gls{er}, \gls{egfr}, \gls{pr}, p53, Src and \gls{tgfb}) are related to the underlying biological mechanism that drives the breast tumour development.

With that said, even if these pathway signatures were related to the underlying biology of breast cancer, the fact that these results depended on the pathway associated genetic signatures from the \citet{Gatza2010a} study makes the results questionable.
This was due to the lack of consistency of the metagenes across different cancer data sets, where more than half of the pathway metagenes showed a correlation of less than 0.8 in at least one data set (\cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}).
This meant that at least half of the signatures were specific to the GT data set and could be highly variable in the other data sets, reflecting the potential differences in the cohorts (at the molecular level).
Thus, without further validation of the quality of the pathway associated genetic signatures and verification of the roles of these signatures in the biological relationship between obesity and cancer, these results should be interpreted with care.

### 2017-03-23 thesis/thesis.tex
Almost finished editing discussion - tmp commit
Finished editing the draft thesis - clean things up
tmp commit

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttablex}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
% \includeonly{{./intro/intro}}
\includeonly{{./methods/methods},{./results/results2},{./misc/appendix2}}
% \includeonly{{./results/results}}
% \includeonly{{./results/results2}}
% \includeonly{{./discussion/discussion}}
% \includeonly{{./misc/appendix}}
% \includeonly{{./misc/appendix2}}

\defcitealias{TCGA}{NCI and NHGRI, 2016}
\defcitealias{ICGC}{ICGC, 2016}
\defcitealias{GEO}{NCBI, 2016}

@@

\printglossary[style=altlist]

@@

% Print out the bibliography:
\bibliography{./MSc,./msc2,./msc3}

>>>>

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym,style=super]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttablex}             % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
% \includeonly{{./intro/intro}}
% \includeonly{{./methods/methods}}
\includeonly{{./results/results2},{./discussion/discussion},{./misc/appendix},{./misc/appendix2}}
% \includeonly{{./results/results}}
% \includeonly{{./results/results2}}
% \includeonly{{./discussion/discussion}}
% \includeonly{{./misc/appendix}}
% \includeonly{{./misc/appendix2}}

% Define some alias for very long citations:
\defcitealias{TCGA}{NCI and NHGRI, 2016}
\defcitealias{ICGC}{ICGC, 2016}
\defcitealias{GEO}{NCBI, 2016}

@@

\printglossary[style=super]

@@

% Print out the bibliography:
\bibliography{./MSc,./MSc2,./MSc3}
